The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2009-07-27 script/en/chapters/primes.tex
script-en: port Pari/GP code to Sage; special values in binary and decimal systems

These values can be used, to evaluate from a key length in bit the
according number of possible keys and the search effort (if assumed, that
e.g. one million keys can be tested within one second).

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|l|}\hline
Dual system   &   Decimal system \\
\hline \hline
$2^{10}$ 	& $1024$ \\
$2^{40}$ 	&  $1.09951\cdot 10^{12}$ \\
$2^{56}$ 	&  $7.20576\cdot 10^{16}$ \\
$2^{64}$ 	&  $1.84467\cdot 10^{19}$ \\
$2^{80}$ 	&  $1.20893\cdot 10^{24}$ \\
$2^{90}$ 	&  $1.23794\cdot 10^{27}$ \\
$2^{112}$ 	&  $5.19230\cdot 10^{33}$ \\
$2^{128}$ 	&  $3.40282\cdot 10^{38}$ \\
$2^{150}$ 	&  $1.42725\cdot 10^{45}$ \\
$2^{160}$ 	&  $1.46150\cdot 10^{48}$ \\
$2^{192}$ 	&   $6,27710\cdot 10^{57}$ \\
$2^{250}$ 	&  $1.80925\cdot 10^{75}$ \\
$2^{256}$ 	&  $1.15792\cdot 10^{77}$ \\
$2^{320}$ 	&  $2.13599\cdot 10^{96}$ \\
$2^{512}$ 	&  $1.34078\cdot 10^{154}$ \\
$2^{768}$ 	&  $1.55252\cdot 10^{231}$ \\
$2^{1024}$	&  $1.79769\cdot 10^{308}$ \\
$2^{2048}$	&  $3.23170\cdot 10^{616}$ \\ \hline
\end{tabular}
\caption{Special values of the binary and decimal system}
\end{center}
\end{table}

Such tables can easily be calculated with computer algebra systems.
Here a code sample for the CAS system Pari-GP\index{Pari-GP}\index{CAS}:
\vspace{-2ex}
\begin{verbatim}
v2=[56, 64, 80, 90, 112, 128, 192, 256];
default(format,"e0.6");
for ( i=1,8, o=v2[i]; print(o, " --- ", 1.*2^o) );
\end{verbatim}

>>>>

These values can be used to evaluate from a key length in bit the
corresponding number of possible keys and the search effort (if
assumed, that e.g. one million keys can be tested within one second).

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|l|}\hline
Binary system   &   Decimal system \\
\hline \hline
$2^{10}$ 	& $1024$ \\
$2^{40}$ 	&  $1.09951 \cdot 10^{12}$ \\
$2^{56}$ 	&  $7.20576 \cdot 10^{16}$ \\
$2^{64}$ 	&  $1.84467 \cdot 10^{19}$ \\
$2^{80}$ 	&  $1.20893 \cdot 10^{24}$ \\
$2^{90}$ 	&  $1.23794 \cdot 10^{27}$ \\
$2^{112}$ 	&  $5.19230 \cdot 10^{33}$ \\
$2^{128}$ 	&  $3.40282 \cdot 10^{38}$ \\
$2^{150}$ 	&  $1.42725 \cdot 10^{45}$ \\
$2^{160}$ 	&  $1.46150 \cdot 10^{48}$ \\
$2^{192}$ 	&  $6,27710 \cdot 10^{57}$ \\
$2^{250}$ 	&  $1.80925 \cdot 10^{75}$ \\
$2^{256}$ 	&  $1.15792 \cdot 10^{77}$ \\
$2^{320}$ 	&  $2.13599 \cdot 10^{96}$ \\
$2^{512}$ 	&  $1.34078 \cdot 10^{154}$ \\
$2^{768}$ 	&  $1.55252 \cdot 10^{231}$ \\
$2^{1024}$	&  $1.79769 \cdot 10^{308}$ \\
$2^{2048}$	&  $3.23170 \cdot 10^{616}$ \\ \hline
\end{tabular}
\caption{Special values of the binary and decimal systems}
\end{center}
\end{table}

\noindent Such tables can easily be calculated using computer algebra
systems. Here is a code sample for Sage\index{Sage}\index{CAS}:

\begin{sagecode}
\begin{Verbatim}%
[fontsize=\footnotesize,fontshape=tt]
sage: E = [10, 40, 56, 64, 80, 90, 112, 128, 150, 160, 192, 256, 1024, 2048]
sage: for e in E:
....:     print "2^" + str(e), "---", 1.0*(2^e)
....:     
2^10 --- 1024.00000000000
2^40 --- 1.09951162777600e12
2^56 --- 7.20575940379279e16
2^64 --- 1.84467440737096e19
2^80 --- 1.20892581961463e24
2^90 --- 1.23794003928538e27
2^112 --- 5.19229685853483e33
2^128 --- 3.40282366920938e38
2^150 --- 1.42724769270596e45
2^160 --- 1.46150163733090e48
2^192 --- 6.27710173538668e57
2^256 --- 1.15792089237316e77
2^1024 --- 1.79769313486232e308
2^2048 --- 3.23170060713110e616
\end{Verbatim}
\caption{Special values of the binary and decimal systems}
\end{sagecode}
